---
title: "workshop9-collab"
format: html
---

load libraries

```{r}
library(tidyverse) # Loading wrangling and plotting packages
library(lterdatasampler) # Loading for data access
library(ggeffects) # Loading for models
library(here) # loading for easy file pathing
```

reading in data

```{r}
data(pie_crab) # reading in plum island ecosystem crab data set from package
```

exploratory vis

```{r}
ggplot(data = pie_crab, aes(x = latitude, y = size)) + # set up plot
  geom_point(color = "orange") + # orange scatterplot
  labs(x = "Latitude", y = "Size (millimeters)") + # update axis labels
  theme_minimal()
```

writing a model

```{r}
crab_model <- lm(size ~ latitude, # formula: response ~ predictor
                 data = pie_crab)

par(mfrow=c(2, 2))
plot(crab_model)
```

interpret model

```{r}
summary(crab_model) # check results
```

Slope: 0.49 +/- 0.034

Y-Intercept: -3.6 +/- 1.27

For every one unit increase in latitude, we expect to see an increase in crab size of 0.49 +/- 0.034 millimeters.

Model statistics: F(1, 390) = 208.5, p \< 0.001, alpha = 0.05, R&2 = 0.35.

General tips for collaboration
1. Always save and commit and push !!!!
2. Talk to your collaborators
3. Pull changes!!! otherwise you will get a "merge conflice"

order of operation
pull, change, save, stage, commit, push